Clustering Constraints on the Relative Sizes of Central and Satellite Galaxies

### 2017-11-27 paper/submission_notes.tex
Brought in changes from arXiv_submission1 branch after removing tarball that was uploaded to arXiv and over-writing the merge commit - this is to keep the size of the master branch from becoming too large

\documentclass[usenatbib,usegraphicx,letterpaper]{mn2e}
%\usepackage[totalwidth=480pt,totalheight=680pt]{geometry}

\usepackage{lmodern}

\usepackage{amsmath}
\usepackage{amstext}
\usepackage{amssymb}
\usepackage{yfonts}

\usepackage{epsfig}
\usepackage{graphicx}
\usepackage{color}

\usepackage[lowtilde]{url}
\usepackage{hyperref}

\bibliographystyle{mn2e}

%-------- journals
\newcommand{\araa}{ARAA~}
\newcommand{\apj}{ApJ~}
\newcommand{\apjl}{ApJL~}
\newcommand{\apjs}{ApJS~}
\newcommand{\mnras}{MNRAS~}
\newcommand{\nat}{Nature~}
\newcommand{\physrep}{Phys. Rep.~}
\newcommand{\aj}{AJ~}
\newcommand{\pasp}{ASP~}

%%%% Misc %%%
\newcommand{\beq}{\begin{equation}}
\newcommand{\eeq}{\end{equation}}
\newcommand{\beqray}{\begin{eqnarray}}
\newcommand{\eeqray}{\end{eqnarray}}

\newcommand{\ben}{\begin{enumerate}}
\newcommand{\een}{\end{enumerate}}
\newcommand{\bit}{\begin{itemize}}
\newcommand{\eit}{\end{itemize}}

%%%%%%%%  galaxy properties  %%%%%%%%
\newcommand{\rhalf}{R_{1/2}}
\newcommand{\rhalfdisk}{R_{1/2}^{\rm disk}}
\newcommand{\rhalfbulge}{R_{1/2}^{\rm bulge}}
\newcommand{\adisk}{A_{\rm disk}}
\newcommand{\abulge}{A_{\rm bulge}}
\newcommand{\alphadisk}{\alpha_{\rm disk}}
\newcommand{\alphabulge}{\alpha_{\rm bulge}}
\newcommand{\sigmarhalf}{\sigma_{\rm R_{1/2}}}
\newcommand{\bt}{{\rm B/T}}
\newcommand{\mstar}{M_{\ast}}
\newcommand{\ssfr}{{\rm sSFR}}
\newcommand{\sfr}{{\rm SFR}}
\newcommand{\fsat}{F_{\rm sat}}

%%%%%%%%  halo properties  %%%%%%%%
\newcommand{\halospin}{\lambda_{\rm halo}}
\newcommand{\mvir}{M_{\rm vir}}
\newcommand{\macc}{M_{\rm acc}}
\newcommand{\mpeak}{M_{\rm peak}}
\newcommand{\zpeak}{z_{M_{\rm peak}}}
\newcommand{\mhalo}{M_{\rm halo}}
\newcommand{\mhost}{M_{\rm host}}
\newcommand{\rvir}{R_{\rm vir}}
\newcommand{\rmpeak}{R_{\rm M_{peak}}}
\newcommand{\vmaxmpeak}{V_{\rm peak}}
\newcommand{\vmax}{V_{\rm max}}
\newcommand{\rspeak}{{R_{\rm s,}}_{\rm M_{peak}}}

%%%%%%%%  cosmology  %%%%%%%%
\newcommand{\lcdm}{\Lambda{\rm CDM}}

%%%%%%%%  observations  %%%%%%%%
\newcommand{\rproj}{r_{\rm p}}
\newcommand{\wproj}{w_{\rm p}}
\newcommand{\wplarge}{w_{\rm p}^{\rm large}}
\newcommand{\wpsmall}{w_{\rm p}^{\rm small}}
\newcommand{\wpall}{w_{\rm p}^{\rm all}}
\newcommand{\mean}[2]{\langle{#1}\vert{#2}\rangle}
\newcommand{\median}[2]{\langle{#1}\vert{#2}\rangle_{\rm median}}

%%%%%%%%  units  %%%%%%%%
\newcommand{\kpc}{{\rm kpc}}
\newcommand{\mpc}{{\rm Mpc}}
\newcommand{\msun}{M_\odot}
\newcommand{\kms}{{\rm km/s}}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\usepackage{epsfig}  \usepackage{graphicx}   \usepackage{rotating}

\begin{document}

\title[The Relative Sizes of Centrals and Satellites]
{Clustering Constraints on the Relative Sizes of Central and Satellite Galaxies}

\author[Hearin, Behroozi, Kravtsov \& Moster]{
Andrew Hearin$^{1}$, Peter Behroozi$^{2}$, Andrey Kravtsov$^{3}$, Benjamin Moster$^{4,5}$\\
$^{1}$Argonne National Laboratory, Argonne, IL, USA 60439, USA\\
$^{2}$Department of Physics, University of Arizona, 1118 E 4th St, Tucson, AZ 85721 USA\\
$^{3}$Department of Astronomy \& Astrophysics, and Kavli Institute for Cosmological Physics, The University of Chicago, Chicago IL 60637\\
$^{4}$Universit{\"a}ts-Sternwarte, Ludwig-Maximilians-Universit{\"a}t M{\"u}nchen, Scheinerstr. 1, 81679 M{\"u}nchen, Germany\\
$^5$Max-Planck Institut f\"ur Astrophysik, Karl-Schwarzschild Stra\ss e 1, 85748 Garching, Germany
}

\maketitle

\begin{abstract}
We empirically constrain how galaxy size relates to halo virial radius using new measurements of the size- and stellar mass-dependent clustering of galaxies in the Sloan Digital Sky Survey.  We find that small galaxies cluster much more strongly than large galaxies of the same stellar mass. 
The magnitude of this clustering difference increases on small scales, and decreases with increasing stellar mass. 
Using {\tt Halotools} to forward model the observations, we test an empirical model in which present-day galaxy size is 
proportional to the size of the virial radius at the time the halo reached its maximum mass. This simple model reproduces the 
observed size-dependence of galaxy clustering in striking detail. 
The success of this model provides strong support for the conclusion that satellite galaxies have smaller sizes relative to central 
galaxies of the same halo mass. 
Our findings indicate that satellite size is set prior to the time of infall, and that a remarkably simple, linear size--virial radius relation 
emerges from the complex physics regulating galaxy size. 
We make quantitative predictions for future measurements of galaxy-galaxy lensing, including dependence upon size, scale, 
and stellar mass, and provide a scaling relation of the ratio of mean sizes of satellites and central galaxies as a function of their halo mass 
that can be used to calibrate hydrodynamical simulations and semi-analytic models. 
\end{abstract}

%----------------------------
\section{Introduction}
\label{sec:intro}
%----------------------------

Many properties of observed galaxies exhibit remarkably tight scaling relations. Galaxy size, typically quantified by a half-mass or half-light radius, $\rhalf,$ has well-measured scaling with galaxy mass $\mstar$ in the local Universe \citep{shen_etal03,huang_etal13,lange_etal15,zhang_yang17}, and at higher redshift \citep{trujillo_etal04,huertas_company_etal13a,vanderwel_etal14,kawamata_etal15,shibuya_etal15,huang_etal17}.

Observational constraints on models for galaxy size typically come from one-point function measurements such as $\mean{\rhalf}{\mstar}$ and $\sigma(\rhalf\vert\mstar),$ e.g.,  \citet{khochfar_silk06,lang_etal14,desmond_etal17,bottrell_etal17b,hou_etal17,somerville_etal17}, or otherwise from catalogs of galaxy groups \citep{weinmann_etal08,guo_etal09,huertas_company_etal13b,spindler_wake17}. More recently, the connection between a galaxy's size and the virial radius of its parent halo has been
explored by converting stellar mass to halo mass and virial radius, using abundance matching \citep{kravtsov_etal04,tasitsiomi_etal04,vale_ostriker04,vale_ostriker06,conroy_etal06}.  Such analyses have indicated that galaxy size is, on average, proportional to host halo virial radius, both at $z=0$ \citep{kravtsov13}, and higher redshifts \citep{huang_etal17,somerville_etal17}.

Observations of two-point galaxy clustering, $\wproj(\rproj),$ have historically been used to place tight constraints on many features of the galaxy--halo connection, such as its $\mstar-$dependence \citep{moster_etal10,leauthaud_etal11,reddick_etal13,skibba_etal15}, dependence on luminosity \citep{kravtsov_etal04, tasitsiomi_etal04,vale_ostriker04,vale_ostriker06,tinker_etal05,cacciato_etal13}, broadband color \citep{coil_etal08,zehavi_etal11,guo_etal11,hearin_watson13}, and star-formation rate \citep{wang_etal07,tinker_etal13,watson_etal14}. In the present work, we exploit the constraining power of $\wproj(\rproj)$ to test empirical models connecting galaxy stellar mass and size to the properties of the galaxy's parent dark matter halo.

The approach we take is to forward model the $\rhalf-$halo connection: we generate Monte Carlo realizations of models using a high-resolution cosmological $N$-body simulation, and then make synthetic measurements in a manner that closely mimics the measurements we make on observed galaxies. We describe the dataset and simulations we use in \S\ref{sec:data}. Our forward-modeling methods are described in \S\ref{sec:model}, with supplementary material in the Appendix. All of our primary results appear in \S\ref{sec:results}, and their theoretical interpretation in \S\ref{sec:interpretation}. We contextualize our findings in terms of previous work in \S\ref{sec:previous_work}, and discuss future directions in \S\ref{sec:future}. We conclude the paper with a summary of our principal results in \S\ref{sec:conclusion}.

%---------------------------------------------------------------------------------------------------
\begin{figure*}
\centering
\includegraphics[width=9cm]{FIGS/sdss_size_vs_mstar_scatter.pdf}
\includegraphics[width=\textwidth]{FIGS/sdss_small_large_sample_definitions.pdf}
\caption{
{\bf Definition of ``small" and ``large" galaxies.} For a volume-limited SDSS galaxy sample defined by $M_{\ast}>10^{10.25}M_{\odot},$ the {\em top panel} visually demonstrates how we classify galaxies into ``small" and ``large" subsamples in an $\mstar$-dependent manner. As described in detail in \S\ref{subsec:sizedef}, we compute the median value $\median{\rhalf}{\mstar}$ at the stellar mass of each galaxy in the sample, and divide the sample into two based on this $\mstar-$dependent cut. The {\em bottom left panel} compares the stellar mass functions $\phi(\mstar)$ of the two samples, confirming that our method for separating ``small" from ``large" galaxies yields subsamples with statistically indistinguishable $\phi(\mstar)$. The {\em bottom right panel} shows histograms of $\rhalf$ for the two subsamples, which partially overlap due to the stellar mass range spanned by the sample.
}
\label{fig:sizedefinition}
\end{figure*}
%-----------------------------------------------------------------------------------------------------

%-----------------------------------------
\section{Data and Simulations}
\label{sec:data}
%-----------------------------------------

The starting point for our galaxy samples comes from Data Release 10 of the Sloan Digital Sky Survey \citep[SDSS,][]{ahn_etal14}, with stellar mass measurements taken from the MPA-JHU catalog \citep{kauffmann_etal03,brinchmann_etal04}. Discarding galaxies with redshift $z<0.02,$ we define volume-limited, $\mstar-$threshold samples by applying a maximum-redshift cut $z_{\rm max}$ appropriate for the $\mstar$ threshold; we use the same $z_{\rm max}$ cut shown in Figure 2 of \citet{behroozi_etal15}.

We supplement the MPA-JHU catalog with measurements of half-light radius, $\rhalf,$ derived from galaxy profile decompositions provided by \citet{meert_etal15}. The \citet{meert_etal15} catalog is based on Data Release 7 of SDSS \citep{abazajian_etal09}, with improvements to the photometry pipeline and light profile fitting method and, especially, in background subtraction \citep{vikram_etal10,bernardi_etal13,bernardi_etal14,meert_etal13}. In the version of this catalog that we use,\footnote{Our $\mstar$ and $\rhalf$ measurements are derived from different photometry pipelines; this is driven by our desire for consistency with the \citet{behroozi_etal15} completeness cuts used in our clustering measurements. We note that we have repeated our analysis for stellar mass measurements based on \citet{meert_etal15}, finding only minor quantitative, and no qualitative changes to our results.} two-dimensional $r-$band profiles were fit with a two-component de Vaucouleurs + exponential profile to determine the projected half-light radius of total $r-$band luminosity, $\rhalf.$

As the bedrock of our modeling, we use the publicly available\footnote{\url{http://www.slac.stanford.edu/~behroozi/BPlanck\_Hlists}} catalog of {\tt Rockstar} subhalos identified at $z=0$ in the Bolshoi-Planck simulation \citep{klypin_etal11,klypin_etal16,behroozi12_rockstar,riebe_etal13,behroozi_etal12b,rodriguez_puebla16_bolplanck}. As described in \S\ref{subsec:sham}, we use traditional abundance matching to connect stellar mass $\mstar$ with masses of halos and subhalos. To address issues related to subhalo incompleteness \citep{guo_white13,campbell_etal17}, we supplement the Bolshoi-Planck subhalo catalog with subhalos that have been disrupted and no longer appear in the standard catalog as $z=0$ surviving subhalos. We describe our treatment of these ``orphan" galaxies in the Appendix, where we also show results that exclude all orphan galaxies.

For our SDSS galaxy samples, we calculate two-point clustering $\wproj$ using line-of-sight projection of $\pi_{\rm max}=20~\mpc$ using the {\tt correl} program in {\tt UniverseMachine} (Behroozi et al. 2017, in prep). The {\tt correl} code uses the \citet{landy_szalay93} estimator ($DD - 2DR + RR$) to compute the redshift-space correlation function $\xi(\rproj, \pi)$, which is then integrated over $\vert\pi\vert < 20$ Mpc to compute the projected correlation function $\wproj(\rproj)$.  The code uses $10^6$ randoms drawn from the same mask region with uniform volume distribution to compute $DR$, and $RR$ is computed via Monte Carlo integration. Errors are estimated by jackknife resampling, giving us an estimate for the lower bound of samples with volumes $V_{\rm eff}\lesssim 0.3\,{\rm Gpc}^3.$

For mock galaxies, we compute $\wproj$ using the {\tt mock\_observables.wp} function in {\tt Halotools} \citep{hearin_etal16}, which is a python implementation of the algorithm in the {\tt Corrfunc} C library \citep{sinha_etal17}. We also use {\tt Halotools} to compute the galaxy-galaxy lensing signal, $\Delta\Sigma,$ using the {\tt mock\_observables.delta\_sigma} function.

All numerical values of $\rhalf$ will be quoted in physical $\kpc,$ and all values of $\mstar$ and $\mhalo$ in $\msun,$ assuming $H_0=67.8~\kms\equiv100h~\kms,$ the best-fit value from \citet{planck15}. To scale stellar masses to ``$h=1$ units" \citep{croton13}, our numerically quoted values for $\mstar$ should be multiplied by $h^2,$ while our halo masses and distances should be multiplied by $h.$

\subsection{Classifying large vs. small galaxies}
\label{subsec:sizedef}

Galaxy clustering has well-known dependence upon $\mstar$, which is not the focus of this work.  We thus wish to remove this dependence to focus solely on the  $\wproj(\rproj)$ dependence
on $\rhalf.$ To do so, we determine the value $\median{\rhalf}{\mstar}$ by computing a sliding median of $\rhalf$ for galaxies sorted by $\mstar,$ calculated using a symmetric window of width $N_{\rm gal}=1000,$ keeping this window fixed for the first and last $500$ galaxies. Each galaxy is categorized as either ``large" or ``small" according to whether it is above or below the median value appropriate for its stellar mass. We note that this is analogous to the common convention for studying the properties of ``red" vs. ``blue" galaxies, in which the two subsamples are divided by a $\mstar-$ or luminosity-dependent green valley cut \citep[e.g.,][]{vdB_etal08,zehavi_etal11}, only here the $\rhalf$ distribution is uni-modal, not bi-modal.

Using this technique, for any $\mstar-$threshold sample, the stellar mass function of the ``large" and ``small" subsamples are identical. We illustrate this for the particular case of $\mstar>10^{10.25}\msun$ in bottom left panel of Figure~\ref{fig:sizedefinition}, which shows stellar mass functions for the two subsamples. The bottom right panel of Figure~\ref{fig:sizedefinition} compares histograms of the two size distributions of these subsamples, which partially overlap due to the variation in $\median{\rhalf}{\mstar}$ across the $\mstar-$ range of the threshold sample.

In addition to stellar mass, $\wproj(\rproj)$ depends on galaxy color \citep[e.g.,][]{zehavi_etal11}. Thus, we will also consider the 
dependence of clustering on galaxy size while controlling for color. Observations of clustering exhibited by subsamples split in stellar mass and color are presented in \S\ref{subsec:colormorph}.

\section{Galaxy-Halo Model}
\label{sec:model}

\subsection{Abundance Matching}
\label{subsec:sham}

We map $\mstar$ onto subhalos using deconvolution abundance matching (SHAM). See Section 3.3 of \citet{behroozi_etal10}, or the appendix of \citet{kravtsov_etal14}, for an account of the mathematics underlying this technique in the presence of scatter. To perform the abundance matching, we use the publicly available code\footnote{\url{https://bitbucket.org/yymao/abundancematching}} developed by Yao-Yuan Mao \citep{lehmann_etal15} that provides a python wrapper around the C kernel developed in \citet{behroozi_etal10}. For the subhalo property used in SHAM, we use $\mpeak,$ the largest value of $\mvir$ ever attained by the subhalo throughout the entire history of the main progenitor halo.  Using the stellar mass function provided in \citet{moustakas_etal13}, we model $\mstar$ as a log-normal distribution with $0.2$ dex of scatter about the median relation $\median{\mstar}{\mpeak}$ determined by SHAM \citep{reddick_etal13}. As described in the appendix, we include a prescription for supplementing the ordinary {\tt Rockstar} subhalo catalog with disrupted subhalos, so that some of our model galaxies inhabit subhalos that are no longer resolved and do not appear in the standard publicly available catalog (``orphan galaxies").

Figure \ref{fig:baseline_sham_clustering} shows that our implementation of SHAM produces model galaxies whose projected clustering is in reasonably good agreement with SDSS galaxies. We note, however, that small-scale clustering shows mild $\sim10-20\%$ tension at stellar mass $\mstar\gtrsim10^{10.75}\msun,$ and similarly on all scales for the $\mstar\gtrsim10^{9.75}\msun$ sample, although the statistical significance of this discrepancy is likely rather mild due to the sample variance of SDSS galaxies with $z\lesssim0.05.$

%---------------------------------------------------------------------------------------------------
\begin{figure}
\centering
\includegraphics[width=8cm]{FIGS/baseline_sham.pdf}
\caption{
{\bf Abundance matching clustering predictions.}
We show the $\mstar-$dependence of projected galaxy clustering, $\wproj(\rproj),$ comparing standard abundance matching to SDSS galaxies (see \S\ref{subsec:sham} for details). Each panel shows the comparison for a volume-limited sample defined by a different $\mstar-$threshold. Black points with error bars show SDSS measurements; solid black curves show the abundance matching prediction of our fiducial model, which includes the effect of orphan subhalos (see Appendix A). Including orphans mitigates the discrepancy in the clustering predicted by traditional, $\mpeak-$based SHAM, though mild tension remains on small scales for $\mstar\gtrsim10^{10.75}\msun,$ and on all scales for $\mstar\gtrsim10^{9.75}\msun.$
}
\label{fig:baseline_sham_clustering}
\end{figure}
%-----------------------------------------------------------------------------------------------------

\subsection{Galaxy size models}
\label{subsec:model}

Our primary results in \S\ref{sec:results} show predictions for the $\rhalf-$dependence of galaxy clustering for two classes of empirical models, described in turn in the two subsections below.

\subsubsection{$\mstar$-based model with satellite mass loss}
\label{subsubsec:strippingmodel}

In the first model we assume that stellar mass $\mstar$ controls $\rhalf.$ To implement this model, for simplicity we tabulate $\median{\rhalf}{\mstar}$ directly from the data, rather than pursue a parametric form, so that this model reproduces the observed $\rhalf-\mstar$ relation by construction. In order to ensure that the model has a level of scatter in $\rhalf$ at fixed $\mstar$ that is comparable to the level reported in \citet{somerville_etal17}, our model sizes are drawn from a log-normal distribution with $0.2$ dex of scatter centered at the observed $\median{\rhalf}{\mstar}.$

It is natural to consider the possibility that stellar mass is stripped from satellite galaxies after infall. The basis for our implementation of this phenomenon is the fitting function presented in \citet{smith_etal16}, which was calibrated by studying stellar mass loss in a suite of high-resolution hydrodynamical simulations. In this model, $f_{\ast}$ quantifies the remaining fraction of stellar mass as a function of $f_{\rm DM},$ the fraction of dark matter mass that remains after subhalo infall:
\beq
f_{\ast} = 1 - \exp(-14.2f_{\rm DM}).
\eeq
For $f_{\rm DM}$ we use the ratio of present-day subhalo mass divided by the peak mass, $M_{\rm vir}/M_{\rm peak}.$ If we denote the post-stripping stellar mass as $M_{\ast}',$ then we have $M_{\ast}'\equiv f_{\ast}M_{\ast},$ where $M_{\ast}$ is given by the initial application of abundance matching. We then calculate the post-stripping radius by interpolating $\langle\rhalf'\vert\mstar'\rangle$ directly from SDSS data. In this way, we model satellite mass loss and  size truncation in a manner that mimics what is seen in hydrodynamical simulations. As shown in \citet{smith_etal16}, stellar stripping in this model does not begin until $f_{\rm DM}\lesssim0.2,$ and in order for $\sim50\%$ of stars to be stripped, the DM halo needs to be stripped to $\sim5\%$ of its initial mass.

\subsubsection{$\rvir-$based model}
\label{subsubsec:rvirmodel}

%---------------------------------------------------------------------------------------------------
\begin{figure}
\centering
\includegraphics[width=8cm]{FIGS/rvir_only_rhalf_vs_mstar_sham_model.pdf}
\caption{
The black curve shows the median size-mass relation of SDSS galaxies as measured in \citet{meert_etal15}. The two gray bands enveloping the black curve show the $50\%$ and $90\%$ percentile regions. The blue curve shows the $\rvir-$based model in which $\median{\rhalf}{\rvir}=0.01\rvir$ (see Section \ref{subsubsec:rvirmodel} for details).  
}
\label{fig:scatter_plot}
\end{figure}
%-----------------------------------------------------------------------------------------------------

As noted in \S\ref{sec:intro}, it was shown in \citet{kravtsov13} that galaxy sizes are on average proportional to the virial radius of their host halo. Motivated by these results, we  explore a model in which $\rhalf$ scales linearly with halo virial radius:\footnote{We note that the normalization factor in \citet{kravtsov13} is 0.015, whereas our normalization is 0.01. The difference derives from two factors: {\em i.} the choice of halo radius definition: \citet{bryan_norman98} in the present work, compared to the $200c$ definition used in \citet{kravtsov13}; {\em ii.} the latter study used deprojected (larger) sizes for spheroidal galaxies, whereas we make no such correction here. See \S\ref{sec:future} for further discussion.}
\beq
\label{eq:fiducial_model}
\rhalf = 0.01\rvir
\eeq
For the virial radius of halos and subhalos, we use $\rmpeak:$ the value of $\rvir$ in physical units of $\kpc$ measured at the time when halo mass reached its maximum, $\zpeak.$  The relationship between $\rmpeak, \mpeak$ and $\zpeak$ is given by
\beq
\mpeak\equiv\frac{4\pi}{3}\rmpeak^{3}\Delta_{\rm vir}(\zpeak)\rho_{\rm m}(\zpeak),
\eeq
where for $\Delta_{\rm vir}(\zpeak)$ we use the fitting function to the ``virial" definition used in \citet{bryan_norman98}. This modeling assumption effectively defines $\median{\rhalf}{\mhalo};$ this relation defines the center of the log-normal distribution with $0.2$ dex of scatter that we use to generate a Monto Carlo realization of the model population.

%---------------------------------------------------------------------------------------------------
\begin{figure*}
\centering
\includegraphics[width=11cm]{FIGS/rvir_only_wp_large_small_absolute.pdf}
\caption{
{\bf $\rhalf-$dependence of galaxy clustering: comparison to $\rvir$-based model.}
Red and blue points with error bars show our SDSS measurements of the clustering of small and large galaxies, respectively. For each volume-limited sample of $\mstar-$complete galaxies, the small and large subsamples have identical stellar mass functions, as shown in Figure \ref{fig:sizedefinition}. Small galaxies cluster much more strongly relative to large galaxies of the same stellar mass. Solid curves show the clustering predictions of the $\rvir-$based model described in \S\ref{subsubsec:rvirmodel}. The $\rvir-$based model inherits the shortcoming of ordinary abundance matching shown in Figure \ref{fig:baseline_sham_clustering}, although the model faithfully captures the {\em relative} clustering of small vs. large galaxies, as shown in Figure \ref{fig:clustering_ratio_upshot}.
}
\label{fig:rvir_only_clustering_absolute}
\end{figure*}
%-----------------------------------------------------------------------------------------------------

%---------------------------------------------------------------------------------------------------
\begin{figure*}
\centering
\includegraphics[width=11cm]{FIGS/rvir_only_wp_ratios.pdf}
\caption{
{\bf $\rhalf-$dependence of galaxy clustering: comparison to $\rvir$-based model.}
Closely related to Figure \ref{fig:rvir_only_clustering_absolute}, y-axes show {\em clustering strength ratios,} defined as $\delta\wproj/\wproj\equiv(w_{\rm p}^{\rm large} - w_{\rm p}^{\rm small})/w_{\rm p}^{\rm all}.$ Thus a y-axis value of $-0.5$ corresponds to small galaxies being $50\%$ more strongly clustered than large galaxies of the same stellar mass. Solid curves show predictions of the $\rvir-$based model described in \S\ref{subsubsec:rvirmodel}. Normalizing the measurements and predictions by $w_{\rm p}^{\rm all}$ scales away the shortcoming of ordinary abundance matching (see Figure \ref{fig:baseline_sham_clustering}), highlighting the successful prediction of the $\rvir-$based model for the $\rhalf-$dependence of galaxy clustering.
}
\label{fig:clustering_ratio_upshot}
\end{figure*}
%-----------------------------------------------------------------------------------------------------

%-----------------------
\section{Results}
\label{sec:results}
%-----------------------

%--------------------------------------------------------
\subsection{Size-Mass Scaling Relation}
\label{subsec:one_point_function}
%-------------------------------------------------------

In Figure \ref{fig:scatter_plot} we show the scaling of galaxy size $\rhalf$ with $\mstar.$ The black curve enveloped by the gray bands shows the scaling relation for SDSS galaxies, while the blue curve shows the median relation  $\median{\rhalf}{\mstar}$ predicted using the $\rvir-$based model described in \S\ref{subsubsec:rvirmodel}. While the curvature of the median relation in the model is slightly weaker than SDSS, this figure shows that models in which $\rhalf\propto\rvir$ can nonetheless match the observed $\rhalf-\mstar$ relation remarkably well given only a single parameter, confirming the results of \citet{kravtsov13} in a forward modeling context.

%---------------------------------------------------------------------------
\subsection{Size-Dependent Clustering Measurements}
\label{subsec:clustering_results}
%---------------------------------------------------------------------------

In Figure~\ref{fig:rvir_only_clustering_absolute}, we present new measurements of the $\rhalf-$dependence of projected galaxy clustering, $\wproj(\rproj).$ We measure $\wproj(\rproj)$ separately for large and small subsamples for four different $\mstar$ thresholds: an  $\mstar>10^{9.75}\msun$ sample with $z_{\rm max}=0.0435$ and $N_{\rm gal}=27658;$ an  $\mstar>10^{10.25}\msun$ sample with $z_{\rm max}=0.0663$ and $N_{\rm gal}=48571;$ 
an  $\mstar>10^{10.75}\msun$ sample with $z_{\rm max}=0.1$ and $N_{\rm gal}=52350;$ 
and an  $\mstar>10^{11}\msun$ sample with $z_{\rm max}=0.1$ and $N_{\rm gal}=33578.$ For each threshold, we split the galaxies into ``large" and ``small" subsamples, as described in \S\ref{subsec:sizedef}. As shown in Figure \ref{fig:sizedefinition}, our size-based samples  have similar stellar mass functions. Red points with jackknife-estimated error bars show SDSS measurements of $\wproj(\rproj)$ for samples of small galaxies, while blue points show the measured correlation functions for samples of large galaxies. Solid curves show $\wproj$ as predicted for these subsamples by the $\rvir-$based model of galaxy sizes described in \S\ref{subsubsec:rvirmodel}.

The salient feature of these clustering measurements is that small galaxies cluster more strongly than large galaxies of the same stellar mass in all but the largest $\mstar$ samples. Remarkably, both the trend and the quantitative difference in the shape of the correlation functions of small and large galaxy samples are reproduced by the $\rvir-$based model. This may be surprising, since $\rhalf\propto\rvir,$ halo mass $\rvir\propto\mhalo^{1/3},$ and clustering strength of halos increases with $\mvir.$ Based on this simple argument, one would expect that large galaxies would be the more strongly clustered. We provide a resolution to this conundrum in \S\ref{subsec:censat_sizes}. However,  before doing so, we first examine the clustering test of the $\rvir-$based model in more detail.

As shown in Figure \ref{fig:baseline_sham_clustering}, the abundance matching prediction for $\wproj(\rproj)$ exhibits tension with SDSS observations at the $10-20\%$ level. This tension is inherited by our $\rvir-$based model for size, which is the subject of this work, and so we wish to compare our size models to data in such a way that minimizes the role played by the underlying stellar-to-halo-mass relation. We accomplish this using the {\em $\rhalf$ clustering ratios,} described below.

For each volume-limited $\mstar-$threshold sample, we additionally measure $\wproj(\rproj)$ {\em without} splitting on size, giving us measurements $\wpall, \wplarge,$ and $\wpsmall$ for each threshold sample. This allows us to compute the ratio $(\wplarge-\wpsmall)/\wpall,$ which we refer to as {\em the $\rhalf$ clustering ratio}. These ratios, denoted as $\delta\wproj/\wproj,$ are the measurements appearing on the y-axis in each panel of Figure \ref{fig:clustering_ratio_upshot}. As a specific example, a clustering ratio of $-0.5$ corresponds to small galaxies being $50\%$ more strongly clustered than large galaxies of the same stellar mass.

The points and curves in Figure \ref{fig:clustering_ratio_upshot} are almost all negative: small galaxies cluster more strongly relative to large. This presentation of the measurement makes it clear that the underlying signal of $\rhalf-$dependent clustering is strongest for samples with smaller stellar mass; as $\mstar$ increases, the signal weakens and nearly vanishes for $\mstar\gtrsim10^{11}\msun.$ Strikingly, the $\rvir-$based model reproduces this $\mstar-$dependent behavior, as well as the scale-dependence of the observed clustering signal at each $\mstar.$ As described in \S\ref{subsec:censat_sizes} below, we attribute the success of this prediction to the systematic difference between the sizes of central and satellite galaxies.

%--------------------------------------------------------------------------
\subsection{Testing the Impact of Satellite Mass Loss}
\label{subsec:mstar_stripping}
%--------------------------------------------------------------------------------------
\begin{figure*}
\centering
\includegraphics[width=11cm]{FIGS/alt_model_wp_ratios.pdf}
\caption{
{\bf The subdominant role of tidal stripping.}
In all panels, the axes and points with error bars are the same as in Figure \ref{fig:clustering_ratio_upshot}. The solid green curves show the prediction of a model where $\rhalf$ is statistically set by $\mstar,$ in the complete absence of satellite mass loss. Such a model predicts zero $\rhalf-$dependence to galaxy clustering, in gross tension with observations. The solid purple curves show results for a model in which satellites lose mass after infall in a manner similar to what is seen in high-resolution hydrodynamical simulations, as described in \S\ref{subsubsec:strippingmodel}. This produces satellites that are smaller than centrals, but the effect is too mild to correctly capture the observed clustering. Evidently, satellite-specific mass stripping plays a sub-dominant role in setting the relative size of centrals and satellites.
}
\label{fig:mstarmodelclustering}
\end{figure*}
%-----------------------------------------------------------------------------------------------------

Figure~\ref{fig:mstarmodelclustering} is analogous to Figure \ref{fig:clustering_ratio_upshot}, but instead compares observed clustering ratios to those predicted by models
in which galaxy size is controlled by $\mstar$ (\S\ref{subsubsec:strippingmodel}). Green solid lines show predictions of the $\mstar$-based model that does not account for mass loss due to tides. In this model, $\rhalf$ follows a purely random log-normal distribution, with the median relation $\median{\rhalf}{\mstar}$ directly matched to the observed relation by construction.  This model thus predicts no dependence of galaxy clustering upon $\rhalf$ at fixed $\mstar,$ simply because the scatter of $\rhalf$ about $\median{\rhalf}{\mstar}$ is uncorrelated with any other variable. The figure shows that this model clearly is at odds with the significant dependence of clustering on size exhibited by SDSS galaxies.

Including satellite mass loss in the model introduces correlations in the scatter: after mass loss, satellites have smaller sizes than centrals of the same $\mstar$ due to post-infall tidal stripping.
The purple curves in Figure \ref{fig:mstarmodelclustering} show that satellite mass loss impacts $\rhalf-$dependent clustering in the expected manner. The ``small" galaxy population has a higher satellite fraction due to satellites being smaller than centrals of the same $\mstar,$ and so in this model small galaxies cluster more strongly relative to large. However, the magnitude of the effect is not sufficiently strong  to produce clustering predictions that are consistent with observations.

Due to the shape of ${\rm d}\rhalf/{\rm d}\mstar,$ low-mass satellites have to lose much more halo mass than high-mass satellites in order to get pushed into the small-$\rhalf$ sample. Thus even though there are more satellites at lower masses, the shape of ${\rm d}\rhalf/{\rm d}\mstar$ counteracts this trend, making the mass-dependence of the observed signal shown in Figure \ref{fig:mstarmodelclustering} difficult to explain by appealing to tidal stripping. Evidently, it is difficult to strip enough mass from satellites so that the $\rhalf-$dependent clustering predictions are in agreement with observations.  We reach the same conclusion when we tested an even more extreme $\mstar-$stripping model, in which stellar mass loss is linearly proportional to halo mass loss \citep[][Model 1]{watson_etal12}.
As we argue in \S\ref{sec:interpretation}, this supports the conclusion that the relative difference between median sizes of central and satellite galaxies is largely in place at the time of satellite infall.

%----------------------------------------------------
\subsection{The Role of Galaxy Color}
\label{subsec:colormorph}
%----------------------------------------------------

>>>>

Clustering Constraints on the Relative Sizes of Central and Satellite Galaxies

Andrew Hearin, Peter Behroozi, Andrey Kravtsov, Benjamin Moster

We empirically constrain how galaxy size relates to halo virial radius using new measurements of the size- and stellar mass-dependent clustering of galaxies in the Sloan Digital Sky Survey.  We find that small galaxies cluster much more strongly than large galaxies of the same stellar mass. The magnitude of this clustering difference increases on small scales, and decreases with increasing stellar mass. Using Halotools to forward model the observations, we test an empirical model in which present-day galaxy size is proportional to the size of the virial radius at the time the halo reached its maximum mass. This simple model reproduces the observed size-dependence of galaxy clustering in striking detail. The success of this model provides strong support for the conclusion that satellite galaxies have smaller sizes relative to central galaxies of the same halo mass. Our findings indicate that satellite size is set prior to the time of infall, and that a remarkably simple, linear size--virial radius relation emerges from the complex physics regulating galaxy size. We make quantitative predictions for future measurements of galaxy-galaxy lensing, including dependence upon size, scale, and stellar mass, and provide a scaling relation of the ratio of mean sizes of satellites and central galaxies as a function of their halo mass that can be used to calibrate hydrodynamical simulations and semi-analytic models.

12 pages plus an appendix. Submitted to MNRAS. 
Figure 5 shows that a simple empirical model, with R50 = 0.01Rvir, can accurately reproduce new measurements of size-dependent clustering of SDSS galaxies. Figure 9 shows predictions for the size-dependence of future lensing measurements. Figure 10 provides a diagnostic for hydro sims and SAMs
